%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

First and formost I want to express my sincere gratitude to my advisor, Alexandre Gramfort, PhD., for his valuable guidance, support, encouragements and availability during these 3 short years of my PhD. I also want to thank him for introducing me to such a great multidisciplinary world, it was a great pleasure working on sophisticated problem modeling applied to Neuroscience. Your joy and enthusiasm was motivational for me and thanks for all the funding you made available for going all around world for sake of Science. I would also like to thank, Roland Badeau, PhD., for accepting me in his team, and for our valuable discussions trying to reduce the gap between signal processing communities in both Music and Neuroscience research.\\

Thanks to Daniel Strohmeier, PhD., for his valuable advices at the beginning and all along my PhD, and for his time answering all my questions. I also want to thank Felix Lucka and Joseph Salmon for the awesome project we have got together, it was a great pleasure working with you, where I learned a lot. Also thanks to Virginie van Wassenhove for having me as an external collaborator at Neurospin - CEA Saclay where he have done great work together. I am also grateful for everyone in the MNE development team for their feedbacks of my work and reviewing my code to be integrated.
\\

Thanks to all my colleagues at the "Image, Data, Signal" department at Télécom ParisTech for the awesome working environment. Thanks to my closest colleagues, Mainak Jas, Tom Dupré la Tour, Stanislas Chambon for our several discussions about my work and your valuable feedbacks. It has been a pleasure working and sharing the B412 with you. I also want to thank Thierry Guillemot for introducing the Monday cake, everyone had the chance to discover their cooking skills, and we loved having your lemon pie.\\

Thanks to my music team "Les Airs Andalous" for their support all along my PhD, handling between work and concerts. You are my second family in Paris far away from my home. Thank you.\\

Finally, my family: \\
My parents: Fatima Zohra Benmansour and Mokhtar Bekhti. They gave me my name, they gave me my life, and the motivation of pursuing a PhD. I am so grateful for all your support and for always being here when needed. My siblings: SidiMohamed, Nihel, Abderrahmane and Amina, thank you for the awesome moments living together far from Tlemcen. I miss you already. I am not forgetting the latest Bekhti: Hadi, my nephew who is still 2 years old but still giving me all the inspiration when looking at him. To finish, a big thanks to my beloved, Sami Meziane for his priceless encouragement and patience, you are the best.\\

My final thoughts go to Raghav RV, it was nice having you with us, may you rest in peace.

{\raggedleft Yousra Bekhti\\}
{\raggedleft Paris, November 2017\\}
\end{acknowledgements}